The influence of socioeconomic deprivation on the recovery of urban mobility after COVID-19 in Latin America

### 2024-01-15 manuscript/paper-latin-FUAs.qmd
add journal guidelines

>>>>

[Journal guideline](https://www.nature.com/natcities/content)

Article
An Article is a substantial novel research study of high quality and general interest to urban-focused researchers.

Format:

Title – Up to 90 characters including spaces. Avoid punctuation and active verbs.
Abstract – Up to 150 words, unreferenced. 
Main text – Up to 4,000 words, divided as follows: 
Introduction (without heading)
Results
Discussion
Methods – Up to 3,000 words, following the main text as a separate section. It can include further conceptual framing to justify research design.
References – As a guideline, we typically recommend up to 50. Please follow Nature's reference style.
Display items – Up to 6 figures and/or tables (additional items should go in a separate Supplementary Information file).
